A Fast and Tight Heuristic for A* in Road Networks

### 2020-09-09 paper/ch_potentials.tex
add line numbers
better anonymous author

\pdfinfo{
/Title (A Fast and Tight Heuristic for A* in Road Networks)
/Author (Foo Bar)
/Keywords (shortest path, road graphs, goal-directed search, contraction hierarchy, heuristic search)
}
\title{A Fast and Tight Heuristic for A* in Road Networks}
\author{Foo Bar}

@@

\begin{document}

>>>>

\usepackage[switch]{lineno}

\pdfinfo{
/Title (A Fast and Tight Heuristic for A* in Road Networks)
/Author (Marvin the Paranoid Android)
/Keywords (shortest path, road graphs, goal-directed search, contraction hierarchy, heuristic search)
}
\title{A Fast and Tight Heuristic for A* in Road Networks}
\author{Marvin the Paranoid Android}

@@

\begin{document}
\linenumbers
